\documentclass[12pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{setspace}

\usepackage[T1]{fontenc}
\usepackage{utopia}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\title{Cover Letter Template}
\author{martinchakchak }
\date{September 2020}

\begin{document}

\noindent
\begin{spacing}{1.125}
    \vfill\noindent
    \begin{tabular}[t]{@{}l} 
      \MakeUppercase{\fontsize{18pt}{5pt}\bf Martin Chak}
    \end{tabular}
    \hfill
    \hspace*{7.5cm}
    \raisebox{0.15cm}[\height][\depth]{
        \begin{tabular}[t]{r}
            martinchakchak@yahoo.ca\\
            (647) 222-3388\\
            linkedin.com/in/martinchak
        \end{tabular}
    }
\end{spacing}

\hrule



\noindent\\
\text{October 5, 2020}

\noindent
{\fontsize{10pt}{5pt}To:}\\
{\bf Canvass Analytics}\\

\begin{text}
    Dear Hiring Manager,\\
    
    It is with great enthusiasm that I express my interest for your job listing for a Software Engineer at Canvass Analytics. As an avid student of all things software and a well-rounded developer, I'm  confident that I would be a valuable asset to the team.
    
    Your job posting mentions that you are looking for candidates who possess proficiency in front and back end development, both of which I am experienced with. I have practical experience with most of the tools in the listing, such as Python, JavaScript and React. Utilizing them for personal projects such as webscrapers, APIs, hosting servers and a personal portfolio website, which you may find on the attached resume. 
    
    On many occasions I have worked with small teams of programmers, in school and at hack-a-thons. One thing I have learned from these team-based projects is the importance of being willingness to always learn. A smaller team means more responsibility and weight each member needs to hold, and these lessons lead me to believe that a job in a startup environment will best start off my career in software development.
    
    I confident that my development experience, strong conceptual education and my perpetual willingness to learn will make me a valuable asset in a start-up environment like Canvass Analytics. I look forward to discussing the position and my qualifications in with you in more detail. Thank you for your time and consideration.\\
    
    Sincerely,\\
    Martin Chak
\end{text}

\end{document}
