\documentclass[12pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{setspace}

\usepackage[T1]{fontenc}
\usepackage{utopia}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\title{Cover Letter Template}
\author{martinchakchak }
\date{September 2020}

\begin{document}

\noindent
\begin{spacing}{1.125}
    \vfill\noindent
    \begin{tabular}[t]{@{}l} 
      \MakeUppercase{\fontsize{18pt}{5pt}\bf Martin Chak}
    \end{tabular}
    \hfill
    \hspace*{7.5cm}
    \raisebox{0.15cm}[\height][\depth]{
        \begin{tabular}[t]{r}
            martin.chak@mail.utoronto.ca\\
            (647) 222-3388\\
            linkedin.com/in/martinchak
        \end{tabular}
    }
\end{spacing}

\hrule



\noindent\\
\text{October 5, 2020}

\noindent
{\fontsize{10pt}{5pt}To:}\\
{\bf Celestica Inc.}\\

\begin{text}
    Dear Hiring Manager,\\
    
    It is with great enthusiasm that I express my interest for your job listing for a student intern in Web Cloud Solutions. As an avid student of all things software and a well-rounded developer, I am  confident that I would be a valuable asset to the company and have much to gain by being at Celestica.
    
    Through my education and self-endeavours, I possess working knowledge with most of the tools in the listing, such as Java, Javascript, HTML, CSS3 and SQL. My experience stems from school work and side projects, such experiences include: creating a large mobile application in a small team of developers, creating and managing my own portfolio website using React and working on a variety of cloud platform applications in hack-a-thons and contests. These experiences have given me much time to practice the software development cycle and has conditioned me to always learn new things. A PEY internship at Celestica would further reinforce my abilities as a programmer and kickstart my career.
    
    I confident that my development experience, strong conceptual education and willingness to learn will make me a valuable asset to the team at Celestica and give me the much needed work experience. I look forward to discussing the position and my qualifications with you in more detail. Thank you for your time and consideration.\\
    
    Sincerely,\\
    Martin Chak
\end{text}

\end{document}
