\documentclass[12pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{setspace}

\usepackage[T1]{fontenc}
\usepackage{utopia}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\title{Cover Letter Template}
\author{martinchakchak }
\date{September 2020}

\begin{document}

\noindent
\begin{spacing}{1.125}
    \vfill\noindent
    \begin{tabular}[t]{@{}l} 
      \MakeUppercase{\fontsize{18pt}{5pt}\bf Martin Chak}
    \end{tabular}
    \hfill
    \hspace*{7.5cm}
    \raisebox{0.15cm}[\height][\depth]{
        \begin{tabular}[t]{r}
            martinchakchak@yahoo.ca\\
            (647) 222-3388\\
            linkedin.com/in/martinchak
        \end{tabular}
    }
\end{spacing}

\hrule



\noindent\\
\text{September 16, 2020}

\noindent
{\fontsize{10pt}{5pt}To:}\\
{\bf Deloitte Canada}\\

\begin{text}
    Dear Hiring Manager,\\
    
    It is with great enthusiasm that I express my interest for a chance to be a PEY Software Developer and work on the Omnia AI project. As a third-year student at The University of Toronto with a 3.77 GPA and numerous side projects, I know my experiences will prove to be an asset to the company.
    
    My skills and experiences would make me a valuable asset to the team. I am well-versed with the required languages and have created numerous projects with all the tools you are looking for. On the attached resume, there is a link to my personal website, built with Javascript and React, which further elaborates on some of the projects I have done. For example, one of these projects was STEM Notes, where I was responsible for all the communication between the front-end and back-end teams; leading to an amazing end product that could use AI to turn handwriting into LaTeX code.
    
    I have worked with many project teams both in and out of school, creating large applications or small scale programs for hack-a-thons. I am known to take initiative on my responsibilities and stay knowledgeable about the task at hand.
    
    I have heard many great things from my peers about the internship experience at Deloitte. I hope I may have a future here, thank you for the consideration and I hope to hear from you soon.\\
    
    Sincerely,\\
    Martin Chak
\end{text}

\end{document}
