\documentclass[12pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{setspace}

\usepackage[T1]{fontenc}
\usepackage{utopia}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\title{Cover Letter Template}
\author{martinchakchak }
\date{September 2020}

\begin{document}

\noindent
\begin{spacing}{1.125}
    \vfill\noindent
    \begin{tabular}[t]{@{}l} 
      \MakeUppercase{\fontsize{18pt}{5pt}\bf Martin Chak}
    \end{tabular}
    \hfill
    \hspace*{7.5cm}
    \raisebox{0.15cm}[\height][\depth]{
        \begin{tabular}[t]{r}
            martinchakchak@yahoo.ca\\
            (647) 222-3388\\
            linkedin.com/in/martinchak
        \end{tabular}
    }
\end{spacing}

\hrule



\noindent\\
\text{October 5, 2020}

\noindent
{\fontsize{10pt}{5pt}To:}\\
{\bf Pulsenics Inc}\\

\begin{text}
    Dear Hiring Manager,\\
    
    It is with great enthusiasm that I express my interest for your job listing for a full-stack developer at Pulsenics Inc. As an avid student of all things software and a well-rounded developer, I'm confident that I would be a valuable asset to the team.
    
    Your job posting mentions that you are looking for a driven full-stack developer to help lead your front-end web architecture. I believe my skills and experience could fulfill this role. I have experience with most of the languages in the listing, including C, C++, Java, Python and Javascript. I have worked on multiple relevant front-end projects such as a personal portfolio project and a mobile-web application where I was tasked with setting up low latency communications between client devices and our servers.
    
    I confident that my development experience, strong conceptual education and my perpetual willingness to learn will make me a valuable asset in a start-up environment like Pulsenics. I look forward to discussing the position and my qualifications in with you in more detail. Thank you for your time and consideration.\\
    
    Sincerely,\\
    Martin Chak
\end{text}

\end{document}
