\documentclass[12pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{setspace}

\usepackage[T1]{fontenc}
\usepackage{utopia}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\title{Cover Letter Template}
\author{martinchakchak }
\date{September 2020}

\begin{document}

\noindent
\begin{spacing}{1.125}
    \vfill\noindent
    \begin{tabular}[t]{@{}l} 
      \MakeUppercase{\fontsize{18pt}{5pt}\bf Martin Chak}
    \end{tabular}
    \hfill
    \hspace*{7.5cm}
    \raisebox{0.15cm}[\height][\depth]{
        \begin{tabular}[t]{r}
            martinchakchak@yahoo.ca\\
            (647) 222-3388\\
            linkedin.com/in/martinchak
        \end{tabular}
    }
\end{spacing}

\hrule



\noindent\\
\text{September 16, 2020}

\noindent
{\fontsize{10pt}{5pt}To:}\\
{\bf RBC}\\

\begin{text}
    Dear Hiring Manager,\\
    
    It is with great enthusiasm that I express my interest for the RBC Software Development PEY Internship positions. As a third-year student at The University of Toronto with a 3.77 GPA and numerous side projects, I know my experiences will prove to be an asset to the company.
    
    I have experience in multiple of the prospective positions in the postings, such as Android, API, web and full-stack development. As is written in my resume and website, I have developed and shown front-end capabilities through working on Android applications and designing and coding my own portfolio website in React. I also have experience with API creation libraries such as Flask and Express, and experience hosting them through Raspberry Pi's, Heroku, AWS, etc. for hackathons, personal websites, and even a spy camera I made to watch my pets.
    
    In the past, I have worked with many teams both in and out of school, creating large applications or small scale programs for competitions. I am known to take initiative on my responsibilities and stay knowledgeable about the task at hand.
    
    I have heard many great things from my peers about the internship experience at RBC. I hope I may have a future here, thank you for the consideration and I hope to hear from you soon.\\
    
    Sincerely,\\
    Martin Chak
\end{text}

\end{document}
